Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_appendix_industry_interaction.tex
Section 5.3 and Appendix F:  spacing. No content change.

\subsection{Description of Opportunity, Challenges, and Obstacles}
The opportunity is to create a catalog of success/failure for current and future software projects to be prepared for transitions and achieve sustainability of the software.

@@

\subsection{Plan for Future Organization}
No concrete plans have been made at this point. If the community can rally behind this topic, some momentum could be built. Those interested should post at \url{https://github.com/WSSSPE/meetings/issues/46}

@@

\subsection{Key Milestones and Responsible Parties}
A key portion of this effort will require focused surveys of projects which have succeeded and failed in transition. Both these categories will yield good learning on what works and what does not work. The group has identified what needs to be studied further, but has not identified responsible parties to conduct them.

@@

\subsection{Description of Funding Needed}
Concrete funding needs were not discussed in this working group but a general impression was that some seed funding would motivate members of this group or others in community to launch a survey effort.

>>>>

\subsection{Description of Opportunity, Challenges, and Obstacles}

The opportunity is to create a catalog of success/failure for current and future
software projects to be prepared for transitions and achieve sustainability of
the software.

@@

\subsection{Plan for Future Organization}

No concrete plans have been made at this point. If the community can rally
behind this topic, some momentum could be built. Those interested should post at
\url{https://github.com/WSSSPE/meetings/issues/46}

@@

\subsection{Key Milestones and Responsible Parties}

A key portion of this effort will require focused surveys of projects which have
succeeded and failed in transition. Both these categories will yield good
learning on what works and what does not work. The group has identified what
needs to be studied further, but has not identified responsible parties to
conduct them.

@@

\subsection{Description of Funding Needed}

Concrete funding needs were not discussed in this working group but a general
impression was that some seed funding would motivate members of this group or
others in community to launch a survey effort.

### 2016-02-05 WSSSPE3/report/wg_main_industry_interaction.tex
Section 5.3 and Appendix F:  spacing. No content change.

\begin{enumerate}
\item To complete a set of case studies which look at successful and unsuccessful transitions between academic researchers and industry
\item To create a generalizable framework, which might allow for a broader study of different transition pathways (other than between academia and industry)
\end{enumerate}

@@

\subsubsection{Landing Page}
Transitions Pathways discussions can be posted at \url{https://github.com/WSSSPE/meetings/issues/46} or an email be sent to Nic Weber\footnote{email: \href{mailto:nmweber@uw.edu}{nmweber@uw.edu}} to find out more about the group's efforts and how to participate.

>>>>

\begin{enumerate}

\item To complete a set of case studies which look at successful and
unsuccessful transitions between academic researchers and industry

\item To create a generalizable framework, which might allow for a broader study
of different transition pathways (other than between academia and industry)

\end{enumerate}

@@

\subsubsection{Landing Page}

Transitions Pathways discussions can be posted at
\url{https://github.com/WSSSPE/meetings/issues/46} or an email be sent to Nic
Weber\footnote{email: \href{mailto:nmweber@uw.edu}{nmweber@uw.edu}} to find out
more about the group's efforts and how to participate.
